---
title: "Intro to Fatality Analysis Reporting System Package"
author: "Juan Gabriel Carrasco Bastias"
date: "2023-10-22"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to Fatality Analysis Reporting System Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(packagetestcoursera)
```

# Introduction to the FARS package

This a test package for the couorsere course about building packages. It uses functions that manage data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

An exmaple of the use of this package is the function `fars_read()`, that chack a filename and loads the data.

```{r eval=FALSE}
# Example of the package fars_read

fars_read("data/accident_2013.csv")
```

```{r echo=FALSE}
# load("data/accident_2013.rda")
# print(accident_2013); rm(accident_2013)
packagetestcoursera::fars_map_state()
```
